\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although, SPARQL aficionados might object particularly to the latter point.

@@

The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated. The mappings for OWL 2 and DSP are much more complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.

On the other hand, it can be seen that the higher-level constraint languages are comparatively similar, there seems to be a pattern, a common way to express this type of constraint. Therefore, a mapping from a high-level language to another high-level language would be considerably easier. Unfortunately, there is not (yet) a high-level language that supports all constraint types.

The creation of mappings of constraint languages to SPIN is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. In this example, the validation of the \emph{minimum qualified cardinality restrictions} constraint type is implemented for DSP:

@@

@@

In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language. The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper. The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.

@@

We think that this approach is suitable
\begin{enumerate}
  \item to implement the validation of constraints consistently across constraint languages,
  \item to support the extension of constraint languages by means of a simple mapping, and
  \item to enhance or rather establish the interoperability of different constraint languages.
\end{enumerate}

>>>>

With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.

@@

The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be instantiated to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation of the constraint is NOT a SPIN mapping to implement the constraint, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.

It can be seen that the higher-level constraint languages are comparatively similar, there seems to be a pattern, a common way to express this type of constraint. Therefore, a mapping from a high-level language to another high-level language would be considerably easier. Unfortunately, there is not (yet) a high-level language that supports all constraint types.

The creation of mappings of constraint languages to SPIN to implement their validation is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. In this example, the validation of the \emph{minimum qualified cardinality restrictions} constraint type is implemented for DSP:

@@

The SPIN mappings for OWL 2 and DSP are rather complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.

@@

In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{I do not understand this!} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper. The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.

@@

We think that this approach is suitable
\begin{enumerate}
  \item to implement the validation of constraints consistently across constraint languages,
  \item to support the extension of constraint languages by means of a simple mapping\tb{was genau meinst du damit? wenn weitere constraint typen unterstützt werden sollen?}, and
  \item to enhance or rather establish the interoperability of different constraint languages.
\end{enumerate}
